\documentclass{letter}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\renewcommand{\rmdefault}{ptm} % Times New Roman
\renewcommand{\sfdefault}{phv} % Arial

\signature{. . . . . . . . . . . .}
\address{Harshad Kadam,\\401 Bramha Niwas, AP watluj, \\ Daund, Pune, Maharashtra, \\ Email: \href{mailto:kadamharshad25@gmail.com}{kadamharshad25@gmail.com} \\ Phone: (+91) 7219331137}

\begin{document}

\begin{letter}{PERFICIENT, \\ St. Louis, MO, \\ United States.}

\opening{Hi Team PERFICIENT,}

I am writing to express my interest in the Apigee Developer position at your organization, as advertised on LinkedIn. With 3 years of experience in API management and development, I am confident in my ability to contribute effectively to your team.

During my tenure at Bitwise, I have gained valuable experience in developing and managing APIs using Apigee. I have successfully worked on several projects involving the design, development, and implementation of APIs, resulting in improved efficiency and performance for our client named Global Payments. Additionally, my proficiency in Spring Boot \& Node JS has allowed me to effectively collaborate with cross-functional teams to deliver high-quality solutions on time and within budget.

I am particularly impressed by PERFICIENT's commitment to innovation and mainly the aim of organization (\paragraph{Move Faster | Engage Smarter | Connect Deeper}). I am excited about the opportunity to bring my skills and expertise to your team and contribute to the development of cutting-edge solutions in API management.

Thank you for considering my application. I am looking forward to the possibility of discussing how my background, skills, and enthusiasm can contribute to the success of PERFICIENT. Please find my resume attached for your review.

\closing{Sincerely,\\Harshad Kadam}

\end{letter}

\end{document}
